---
title: "mmyy mmmaaappp"
author: "OSAKUNU ONOME"
date: "May 31, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
```{r}
mapNorcal = leaflet() %>%
 addTiles() %>%
 addMarkers (lat= 37.819722, lng= -122.478611, popup="Golden Gate Bridge")%>%
 addMarkers (lat= 37.4275, lng = -122.1697, popup="Stanford University")%>%
 addMarkers (lat= 37.8719, lng = -122.2585, popup="University of California Berkeley")%>%
 addMarkers (lat= 37.3316, lng= -121.8901, popup="Silicon Valley Tech Museum")
mapNorcal

```

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

